Improvement of crash forces in structures using optimization tools.

### 2016-07-28 paper.tex
Cambios optim strategy

Firstly, with the parametrized model, a sampling of !!N!!\todo{!!} samples is performed, relying on the LHS technique. This method creates a set of data with homogeneous projections on each variable axis, so that no superimposed projections appear.

@@

\subsection{Metrics}
\todo{Plagiado}
The objective of this research is to find a set of optimum designs of the specimen previously described according to three different objective functions. These functions are the absorbed energy ($E_a$), the mass of the specimen ($m$) and the peak load ($P_{peak}$). The three metrics are obtained using a finite element simulation, where $E_a$ and $P_{peak}$ are obtained via the force-displacement curves.

@@

Starting from a baseline model, the optima greatly improve the performance of the model. \Cref{fig:opt_comparison} shows the section of both a baseline model and the single-objective optimum for a maximized SEA. \todo{Te falta el caption. El label ya se lo puse yo.}

\begin{figure}[htpb]
\begin{subfigure}[b]{.45\columnwidth}
   \includegraphics[width=\columnwidth]{figures/IMG/sc1.pdf}
    \caption{Baseline model.}
    \label{fig:back0}
\end{subfigure}
\qquad
\begin{subfigure}[b]{.45\columnwidth}
   \includegraphics[width=\columnwidth]{figures/IMG/topview.png}
    \caption{Specimen with optimum SEA.}
    \label{fig:back5}
\end{subfigure}
\caption{blablabla}
\label{fig:opt_comparison}
\end{figure}

>>>>

Firstly, with the parametrized model, a sampling of !!N!! samples is performed, relying on the LHS technique. This method creates a set of data with homogeneous projections on each variable axis, so that no superimposed projections appear.

@@

\subsection{Metrics}

The objective of this research is to find a set of optimum designs of the specimen previously described according to three different objective functions. These functions are the absorbed energy ($E_a$), the mass of the specimen ($m$) and the peak load ($P_{peak}$). The three metrics are obtained using a finite element simulation, where $E_a$ and $P_{peak}$ are obtained via the force-displacement curves.

@@

Starting from a baseline model, the optima greatly improve the performance of the model. \Cref{fig:opt_comparison} shows the section of both a baseline model and the single-objective optimum for a maximized SEA.

\begin{figure}[htpb]
\begin{subfigure}[b]{.45\columnwidth}
   \includegraphics[width=\columnwidth]{figures/IMG/sc1.pdf}
    \caption{Baseline model.}
    \label{fig:back0}
\end{subfigure}
\qquad
\begin{subfigure}[b]{.45\columnwidth}
   \includegraphics[width=\columnwidth]{figures/IMG/top_view_foam.eps}
    \caption{Specimen with the optimum SEA value.}
    \label{fig:back5}
\end{subfigure}
\end{figure}
